Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-01 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Improved Goodness-of-fit figures

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Touzi1988,oliverquegan98}.
We study two ways of estimating the coefficient of variation.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$."}

@@

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of non-parametric entropy estimators and bootstrap versions.",
    format = "latex",
    booktabs = TRUE,
    align = "crllllllllllll",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table",  position="hbt", linesep = "") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "r")%>%
    kable_styling(latex_options = "scale_down")#%>%
   # kable_styling( full_width = T)
  #)
  #kable_styling(latex_options = c("scale_down"))

@@

The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under null hypothesis is presented alongside running times. 
The test accuracy is evaluated through 1000 simulated samples of different sizes, with each size replicated 100 times using bootstrap resampling.

@@

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density} shows the empirical  densities for different sample sizes  and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical density  under the null hypothesis.", fig.width=6, fig.height=5.0}

@@

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.3) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  #longtable = T,
  booktabs = TRUE,
  align = "ccrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)%>%
  kable_styling(latex_options = c("repeat_header"))

@@

Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution

@@

# Simulación y cálculo de resultados
results_AIC <- data.frame(Test = character(),
                          SampleSize = integer(),
                          Normal = numeric(),
                          Lognormal = numeric(),
                          Gamma = numeric(),
                          Weibull = numeric(),
                          InverseGaussian = numeric())

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
#alpha1 <- -2

@@

# Ajustar las distribuciones a los datos
fln <- fitdist(TestStatistics, "lnorm")
fg <- fitdist(TestStatistics, "gamma")
fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
fw <- fitdist(TestStatistics, "weibull")

# Graficar las comparaciones
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
num_bins <- 86

denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
alpha1 <- -3

@@

# 
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
num_bins <- 86

denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ", xlegend = "topright", ylegend = NULL)
legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV ")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
#alpha1 <- -2

@@

# Ajustar las distribuciones a los datos
fln <- fitdist(TestStatistics, "lnorm")
fg <- fitdist(TestStatistics, "gamma")
fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
fw <- fitdist(TestStatistics, "weibull")

# Graficar las comparaciones
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
 num_bins <- 60

denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

sample.size <- c(49)
R <- 12000
mu <- 1
L <- 5
#B <- 5
alpha1 <- -3

@@

# 
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
num_bins <- 86

denscomp(list( fln, fg, fn, fw), n = num_bins, legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD", xlegend = "topright", ylegend = NULL)
legend("topright", legend = plot.legend, col = c("darkblue", "#637029","indianred3","darkgrey"), lwd = 3, lty = 1, box.lwd = 1,box.col = "white",bg = "white")
# denscomp(list( fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
qqcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)
cdfcomp(list(fln, fg, fn,fw), legendtext = plot.legend, fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3), fitlty = 1,xlab = "CV MnAD")
ppcomp(list(fln, fg, fn,fw), legendtext = plot.legend,fitcol = c("darkblue", "#637029","indianred3","darkgrey"), fitlwd=c(3,3,3,3),xlegend = "topleft", ylegend = NULL)

@@

knitr::include_graphics("../Figures/PNG/H_pvalue_Phantom_4_z1_200b.png")
knitr::include_graphics("../Figures/PNG/cv_pvalues_Phantom_4_z1.png")
knitr::include_graphics("../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1.png")
```
```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$; (\\textbf{b})  $T_\\text{CV}$. (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_005_Phantom_4_z1_AO_200b.png")
knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Phantom_4_z1.png")
knitr::include_graphics("../Figures/PNG/mnad_005_Phantom_7_z1.png")

@@

## SAR Data
<!-- ACF Don't use "real" unless it refers to the real part of a complex value -->
<!-- JA, OK -->
We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
<!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
<!-- ACF Provide the spatial resolution -->
<!-- JA, OK -->
The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco,with $L=18$. (\\textbf{b}) Illinois-Region 1, with $L=36$. \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")

@@

```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

>>>>

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for relating variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met, then the CV is the relative measure that is usually used in real applications. 
The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{Ulaby1986,Touzi1988}.
We study two ways of estimating the coefficient of variation.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$."}

@@

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$.",
    format = "latex",
    booktabs = TRUE,
    align = "crllllllllllll",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table",  position="hbt", linesep = "") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "r")%>%
    kable_styling(latex_options = "scale_down")#%>%
   # kable_styling( full_width = T)
  #)
  #kable_styling(latex_options = c("scale_down"))

@@

The comparison between the bootstrap-improved estimators is shown in Table&nbsp;\ref{tab:table_time}, where the test accuracy under the null hypothesis is presented alongside running times. 
The test accuracy is evaluated through 1000 simulated samples of different sizes, with each size replicated 100 times using bootstrap resampling.

@@

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density} shows the empirical densities obtained by applying  the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 8,11\right\}$ and $\mu=1$. Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, asymmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="hbt",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$ test under the null hypothesis.", fig.width=6, fig.height=5.0}

@@

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.2) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, with $L\\in\\left\\{3,5, 8,11\\right\\}$ and $\\mu=1$.",
  format = "latex",
  #longtable = T,
  booktabs = TRUE,
  align = "ccrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)%>%
  kable_styling(latex_options = c("repeat_header"))

@@

Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots as well as empirical and fitted cumulative distribution functions.
They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.

@@

#
results_AIC <- data.frame(Test = character(),
                          SampleSize = integer(),
                          Normal = numeric(),
                          Lognormal = numeric(),
                          Gamma = numeric(),
                          Weibull = numeric(),
                          InverseGaussian = numeric())

@@

sample.size <- c(49)
R <- 12000
mu <- 1
L <- 5
#B <- 5
#alpha1 <- -2

@@

fln <- fitdist(TestStatistics, "lnorm")
fg <- fitdist(TestStatistics, "gamma")
fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
fw <- fitdist(TestStatistics, "weibull")

par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
#num_bins <- 86

num_bins <- 60 
density_plots <- list(
  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
           fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom")
)

combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
  plot_layout(guides = "collect")

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
B <- 5
alpha1 <- -2

@@

# 
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
num_bins <- 60 
density_plots <- list(
  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
           fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          fitlty = 1, xlab = expression(CV), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom")
)

combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
  plot_layout(guides = "collect")

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
#B <- 5
#alpha1 <- -2

@@

fln <- fitdist(TestStatistics, "lnorm")
fg <- fitdist(TestStatistics, "gamma")
fn <- fitdist(TestStatistics, "norm")  # Ajuste para la distribución normal
fw <- fitdist(TestStatistics, "weibull")

par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
 plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull")

num_bins <- 50 
density_plots <- list(
  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
           fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom")
)

combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
  plot_layout(guides = "collect")

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
#B <- 5
alpha1 <- -3.0

@@

#   colors <- c("#999999", "#E69F00", "#56B4E9", "#009E80", "#009E72","#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#56B4E9", '#999999','#E69F00', "indianred3","#00AFBB", "#E7B800", "#FC4E07")

# 
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot.legend <- c( "Lognormal", "Gamma", "Normal", "Weibull") 
num_bins <- 50 
density_plots <- list(
  denscomp(list(fln, fg, fn, fw), n = num_bins, legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
           fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
           fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  qqcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  cdfcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
          fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
          fitlty = 1, xlab = expression(CV[ MnAD ]), plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom"),

  ppcomp(list(fln, fg, fn, fw), legendtext = c("Lognormal", "Gamma", "Normal", "Weibull"), 
         fitcol = c("darkblue", "#56B4E9", "#FC4E07", "#009E80"), fitlwd = c(1.6, 1.3, 1.2, 1.0),
         plotstyle = "ggplot") +
    theme_minimal() +
    theme(text = element_text(family = "serif"), legend.position = "bottom")
)

combined_plot1 <- wrap_plots(density_plots, ncol = 2) +
  plot_layout(guides = "collect")

@@

knitr::include_graphics("../Figures/PNG/H_pvalue_Phantom_4_z1_200b.png")
knitr::include_graphics("../Figures/PNG/cv_pvalues_Phantom_4_z1.png")
knitr::include_graphics("../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1.png")
```
```{r sim_SAR_Images_p05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_005_Phantom_4_z1_AO_200b.png")
knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Phantom_4_z1.png")
knitr::include_graphics("../Figures/PNG/mnad_005_Phantom_7_z1.png")

@@

## SAR Data

We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
<!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
<!-- ACF Provide the spatial resolution -->
<!-- JA, OK -->
The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$. (\\textbf{b}) Illinois-Region 1, with $L=36$. \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")

@@

```{r test_lake, echo=FALSE, message=FALSE, warning=FALSE,fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Illinois-Region 1: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
